Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
use "Chris J. Ball" for cjb
Hm, I like Internet a bit better than Web.  Call me old-fashioned?
For context: the original idea was that a javascript on a web page would
be able to add a set of new production rules into your local Avatar Services,
since you can't evaluate the preconditions for a new rule set before you
know what they are.  But the distinction between "by visiting a website
some javascript runs to augment your story model" and "downloading from the
Web" is pretty probably not worth being too anal about.  So "incorporated"
may have been a little more accurate in my original draft,

\ifthenelse{\boolean{noauthors}}{}{
\numberofauthors{1}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
C. Scott Ananian \qquad Chris Ball \qquad Michael Stone\titlenote{%
Now at Akamai Technologies.}\\
\affaddr{One Laptop Per Child Foundation}\\
\affaddr{222 Third Street}\\
\affaddr{Cambridge, MA 02142}\\
\email{\{cscott,cjb,mstone\}@laptop.org}
%\and  % use '\and' if you need 'another row' of author names
}
}
\date{12 March 2012}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

Stories consist of a sequence of \textit{scenes} plus information about
characters, locations, and activities.  Scenes are ``goals''
in the STRIPS formalism~\cite{strips} and consist of
action descriptions, preconditions, and effects.
In principle, all preconditions for all scenes of all story modules
are evaluated continuously to determine the actions of the narrative
agents.  This production rules system
is made computationally efficient using the Rete
algorithm.  Dialog is expressed using Curveship-style
templates~\cite{montfort:curveship}.

@@

New story modules can be downloaded from the Web in
connected deployments.  In disconnected deployments, new stories
might be distributed once a year on USB sticks or shared among
friends.  In a classroom environment, a teacher can share stories for
the day's lesson at the start of class.

>>>>

\ifthenelse{\boolean{noauthors}}{}{
\numberofauthors{1}
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
C. Scott Ananian \qquad Chris J. Ball \qquad Michael Stone\titlenote{%
Now at Akamai Technologies.}\\
\affaddr{One Laptop Per Child Foundation}\\
\affaddr{222 Third Street}\\
\affaddr{Cambridge, MA 02142}\\
\email{\{cscott,cjb,mstone\}@laptop.org}
%\and  % use '\and' if you need 'another row' of author names
}
}
\date{12 March 2012}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.

@@

Stories consist of a sequence of \textit{scenes} plus information about
characters, locations, and activities.  Scenes are ``goals''
in the STRIPS formalism~\cite{strips} and consist of
action descriptions, preconditions, and effects.
In principle, all preconditions for all scenes of all story modules
are evaluated continuously to determine the actions of the narrative
agents.  This evaluation
is made computationally efficient using the Rete
algorithm.  Dialog is expressed using Curveship-style
templates, allowing Nell to restructure
expository tense, style, and point-of-view~\cite{montfort:curveship}.

@@

New story modules can be downloaded from the Internet in
connected deployments.  In disconnected deployments, new stories
might be distributed once a year on USB sticks or shared among
friends.  In a classroom environment, a teacher can share stories for
the day's lesson at the start of class.
